---
title: "simpleRegress"
author: "Daniel A Soria Z"
date: "summer 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

I will atempt to find a better model that includes the length of the bear, based on the chest size


```{r}
MYCHEST <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(MYCHEST)
summary.lm(MYCHEST)
```

Based on the comparison of the two models we can say that this model, the MYCHEST model would be more appropriate compaared to the simp model as there was a significant change in the number of the standard error which has gone down and the number for the adjusted R-squared which has gone up as with this model we compare the chest. The number was 4.939 for the standard error and the number for the adjusted R-squared was 0,747 on the other graph. As the adjusted R explains more of the error and the residual standard square is smaller.





```{r}
MYHEADW <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(MYHEADW)
summary.lm(MYHEADW)
```

Using this model, MYHEADW compared to the other model is not as helpfull as the other two in comparison have a smaller Residual standard error and a smaller Adjusted R-squared, as the standard error is of 7.32 and the R-squared is 0.5321 which will allows us to conclude that this model is not as helpful as it wouldnt narrow down on the information more, it would simply make the spread bigger.















